%------------------------
% Resume Template
% Author : Pushp Vashisht
% Github : https://github.com/pushp1997/
% License : MIT
% Inspired By: https://github.com/arasgungore/arasgungore-CV
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Pushp Vashisht}} & Email: \href{mailto:pushp.vashisht@hotmail.com}{pushp.vashisht@hotmail.com}~~~~~\\
  Portfolio: \href{https://pushp.ovh}{pushp.ovh} & Mobile: \href{tel:+3530894890290}{(+353) 0894-890-290}~~~~~~~~~~~~~~~~ \\
  Github:~~ \href{https://github.com/pushp1997}{github.com/pushp1997} & LinkedIn: \href{https://www.linkedin.com/in/pushp-vashisht}{linkedin.com/in/pushp-vashisht} \\
\end{tabular*}

%-----------SKILLS-----------------
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{~~~~~~Python 3, JavaScript, SQL, Bash}
\resumeSubItem{Frameworks}{~~~~Fast API, Django, Flask, Selenium, NodeJS}
\resumeSubItem{Tools}{~~~~~~~~~~~~~~Kubernetes (Rancher / EKS), Docker, GIT, Redis, RabbitMQ, MongoDB, PostgreSQL, MySQL, SQLite, Kibana, FluentD, Elastic Search}
\resumeSubItem{Platforms}{~~~~~~~AWS, Jira, Github, Gitlab}
\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Technical Writing, Adaptibility}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Adcuratio Media Inc}{Bangalore, India}
{Module Lead I}{Apr 2021 - Jun 2022}
\resumeItemListStart
\resumeItemWithoutTitle{Led and mentored a team of 4 developers using Agile Scrum methodologies, including task analysis, breakdown, monitoring, and code evaluation.}
\resumeItemWithoutTitle{Took ownership of a product module and managed the development process to meet business requirements to ensure on time release.}
\resumeItemWithoutTitle{Designed and developed the e-commerce module for Folksmedia, including requirement analysis, system architecture, DB schema, and API pipeline design. Led the successful integration and performance of the module within the overall application.}
\resumeItemWithoutTitle{Developed a full-text search engine with auto-suggestions from scratch, with the ability to search through all products data in approximately 10ms.}
\resumeItem{Roles}{Architecture Design, Backend Development, Requirements Gathering, Task Assigning.}
\resumeItem{Skills Acquired / Utilised}{Python, FastAPI, Docker, Redis, MongoDB.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Adcuratio Media Inc}{Bangalore, India}
{Software Developer}{Apr 2020 - Mar 2021}
\resumeItemListStart
\resumeItemWithoutTitle{Designed and Developed an Ad server from scratch that creates instructions based on the demographic data. These instructions are polled and parsed by televisions to replace an advertisement in real-time with a targeted advertisement. The application is developed with distributed (Kubernetes) architecture in mind and is serving more than 3 million TVs daily in production.}
\resumeItemWithoutTitle{Implemented a graphical dashboard using Kibana to track user impressions through logs data aggregated by FluentD.}
\resumeItemWithoutTitle{Awarded as Best performer employee of the quarter and got promoted skipping multiple ranks within short duration.}
\resumeItem{Roles}{Application Architecture Design, Kubernetes Application development, Cluster Monitoring.}
\resumeItem{Skills Acquired / Utilised}{Python, FastAPI, Rancher (On-Premises k8s cluster provisioning), EKS, Docker, Redis, MongoDB, FluentD, Kibana.}
\resumeItemListEnd
\vspace{2pt}
\resumeSubheading
{Infosys Limited}{Bangalore, India}
{Systems Engineer}{Aug 2019 - Apr 2020}
\resumeItemListStart
\resumeItemWithoutTitle{Worked at the backend of the Infosys Migration Platform, to automate the extraction of business rules from a legacy application code and migration of the legacy application to the latest / desired technologies and worked at the frontend, to create a web user interface to facilitate interaction with the platform.}
\resumeItem{Roles}{Feature Design \& Development, Backend Developer.}
\resumeItem{Skills Acquired / Utilised}{Nodejs, ANTLR, Agile Software Development.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University College Cork}{Cork, Ireland}
{MSc - Computing Science}{2022 - Ongoing}
\vspace{2pt}
\resumeSubheading
{Sikkim Manipal Institute of Technology}{Sikkim, India}
{Bachelor of Technology - Computer Science \& Engineering;  GPA: 7.04}{2015 - 2019}
\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------VOLUNTEERING-----------------
\section{Volunteer Experience}
\resumeSubHeadingListStart
\resumeSubheading{Prayas Foundation}{Renukoot, India}
{Web Developer (Part-time)}{Aug 2019 - Apr 2020}
\resumeItemListStart
\resumeItemWithoutTitle{Developed the website (https://prayasfoundation.org.in), where the user can register to become a donor or request for blood.}
\resumeItemWithoutTitle{My work on this project involved designing and coding the website, as well as testing and debugging to ensure its functionality.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
